\documentclass[9.5pt,a4paper]{article}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{tabularx}
\usepackage{changepage}
\usepackage{fontawesome5}
\geometry{left=0.8cm, right=0.8cm, top=0.5cm, bottom=0.5cm}

\pagestyle{empty}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{0.8em}{0.6em}  % <--- Reduced spacing
\titlespacing*{\subsection}{0pt}{0.5em}{0.1em}

\hypersetup{
    colorlinks=false,            % Disable colored text
    pdfborderstyle={/S/U/W 0.5},   % Underline style, width 1
    pdfborder={0 0 0.5},           % Border width (0 horizontal, 0 vertical, 1 thickness)
    linkbordercolor={0 0 0},     % Black border
    urlbordercolor={0 0 0}       % Black border for URLs
}

\begin{document}

\noindent
\begin{minipage}[t]{0.4\linewidth}
{\Huge \textbf{Harsh Priye}} \\[0.2em]
{\Large Software Developer}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.6\linewidth}
\raggedleft
\faEnvelope~\href{mailto:harsh.rzf@gmail.com}{harsh.rzf@gmail.com} \quad 
\faPhone~\underline{+91-8745946064} \\[0.2em]
\faGlobe~\href{https://harshpriye.in}{harshpriye.in} \quad 
\faGithub~\href{https://github.com/harshpx}{github.com/harshpx} \quad
\faLinkedin~\href{https://linkedin.com/in/harshpx}{linkedin.com/in/harshpx}
\end{minipage}


\section*{Work Experience}
\noindent \textbf{Tata Consultancy Services (TCS)} \hfill \textbf{1 year 3 months} \\
\vspace*{-1em}
\begin{itemize}[left=0.4cm, itemsep=0pt, topsep=0pt, partopsep=0pt]
    \item \textbf{Software Engineer} \hfill \textbf{(Jul 2024 -- Present)}
    \begin{itemize}[left=0cm, itemsep=0pt, topsep=-1pt, partopsep=0pt]
      \setlength{\rightskip}{0.05\textwidth}
      \item Developed secure, scalable APIs for a Forex payments app using Spring-Boot, enabling 1.5 times faster delivery.
      \item Enhanced API efficiency by 40\% via aggregation, query refactoring, pagination, and caching.
      \item Implemented frontend features for a Forex app, enhancing UX and performance in a 6-member team.
      \item Boosted frontend performance by 20\% using lazy loading, state optimization, and improved design patterns.
      \begin{adjustwidth}{-1.2em}{0pt}
        \textbf{Tech Stack:} Java, Spring Boot, Microservices, JavaScript, React.js, Lit Element, Git, Azure
      \end{adjustwidth}
    \end{itemize}
\end{itemize}
\vspace*{0.6em}
\noindent \textbf{AulaCube Technologies } \hfill \textbf{4 months} \\
\vspace*{-1em}
\begin{itemize}[left=0.4cm, itemsep=0pt, topsep=0pt, partopsep=0pt]
    \item \textbf{Software Development Intern} \hfill \textbf{(Mar 2024 -- Jun 2024)}
    \begin{itemize}[left=0cm, itemsep=0pt, topsep=-1pt, partopsep=0pt]
      \setlength{\rightskip}{0.05\textwidth}
      \item Built an admin dashboard for student data, improving readability, management, and client satisfaction by 40\%.
      \item Fixed 30+ irresponsive UI issues on the AulaEdge website for small-screen devices.
      \item Introduced Tailwind CSS to the existing code base for faster and responsive styling.
      \begin{adjustwidth}{-1.2em}{0pt}
        \textbf{Tech Stack:} Typescript, React.js, Ant Design, Chart.js, Git.
      \end{adjustwidth}
    \end{itemize}
\end{itemize}

\section*{Education}
\textbf{B.Tech - Computer Science (Mathematics and Computing)} \hfill \textbf{CGPA: 7.63} \\
Netaji Subhas University of Technology (NSUT), New Delhi \hfill \textbf{(2020 -- 2024)} \\ [0.4 em]
\textbf{AISSCE (CBSE Class 12)} \hfill \textbf{Score: 87\%} \\
Vishwa Bharati Public School, New Delhi \hfill \textbf{(2019 -- 2020)}

\section*{Projects}
\noindent \textbf{Codeboxes - Online Code Editor} \\
\textbf(Java, SpringBoot, Microservices, IPC, MongoDB, Redis, JWT, Next.js, Tailwind CSS, Docker, Github Actions)
\begin{itemize}[left=0.4cm, itemsep=-2pt, topsep=3pt, partopsep=0pt]
  \setlength{\rightskip}{0.05\textwidth}
  \item Developed a full-stack online code editor which supports 6+ major programming languages.
  \item Create REST CRUD APIs using Spring Boot (maintaining REST Maturity Model Level 2), and Configured Spring Security for JWT based authentication and Authorization.
  \item Built a code-execution service with Bash \& Docker, that communicates with the server via IPC (ProcessBuilder).\\Removed dependency on any 3rd party API for code execution entirely (Increased code execution limit to infinity).
  \item Switched to microservice architecture separating User+Auth and Code execution services, improving code execution API availability by 100\% compared to monolith.
  \item Developed frontend with Next.js \& Tailwind, integrating Shadcn UI and Aceternity UI, boosting DAU by 20\%.
  \item Implemented CI/CD pipeline using Docker and Github Actions for 5x faster deployments, compared to manual.
\end{itemize}
\begin{adjustwidth}{2em}{0pt}
\textbf{Source:} \href{https://github.com/harshpx/Codeboxes}{github.com/harshpx/Codeboxes} , \quad
\href{https://github.com/harshpx/codeboxes-server}{github.com/harshpx/codeboxes-server} \\
\textbf{Web url:} \href{https://www.codeboxes.in/}{https://www.codeboxes.in}
\end{adjustwidth}

\vspace*{0.6em}

\noindent \textbf{Mini Tic-Tac-Toe - Online multiplayer tic-tac-toe game} \\
\textbf(Socket.io, Express.js, Node.js, React.js, Tailwind CSS)
\begin{itemize}[left=0.4cm, itemsep=-2pt, topsep=3pt, partopsep=0pt]
  \setlength{\rightskip}{0.05\textwidth}
  \item Structured a bi-directional WebSocket server using Socket.io, to achieve low-latency, real-time communication.\\(90\% faster and less bandwidth usage than constant HTTP polling)
  \item Designed a robust lobby management and scoring system (Only 2 person per lobby, with rematch options).
  \item Also implemented in-game chat using parallel socket connection between both players. Helped gain users by 40\%.
\end{itemize}
\begin{adjustwidth}{2em}{0pt}
\textbf{Source:} \href{https://github.com/harshpx/tic-tac-toe-socket}{github.com/harshpx/tic-tac-toe-socket} \quad \textbf{Web url:} \href{https://mini-tic-tac-toe.vercel.app}{mini-tic-tac-toe.vercel.app}
\end{adjustwidth}

\vspace*{0.6em}

\noindent \textbf{Dog Breed Identifier} \\
\textbf(AI, Machine Learning, Python, Tensorflow, Java, Spring-Boot, TypeScript, Svelte, Sveltekit, Tailwind)
\begin{itemize}[left=0.4cm, itemsep=-2pt, topsep=3pt, partopsep=0pt]
  \setlength{\rightskip}{0.05\textwidth}
  \item Built a CNN image classifier achieving 95\%+ accuracy in classifying dog breeds using Python and TensorFlow.
  \item Served the trained model in a Spring-Boot server to use it as an API.
  \item Migrated from React.js to Svelte for frontend, gaining approx 60\% faster load times and 90\% smaller bundle size. 
\end{itemize}
\begin{adjustwidth}{2em}{0pt}
\textbf{Source:} \href{https://github.com/harshpx/dbi-client}{github.com/harshpx/dbi-client}, \quad \href{https://github.com/harshpx/dbi-server}{github.com/harshpx/dbi-server} \\
\textbf{Web url:} \href{https://dog-breed-identifier-client.vercel.app}{dog-breed-identifier-client.vercel.app} 
\end{adjustwidth}

\section*{Technical Skills / Tech Stack}
\textbf{Languages:} Java, JavaScript, Typescript, Bash, SQL, YAML, HTML, CSS \\
\textbf{Frameworks, Libraries \& tools:} \\
Spring-Boot, Node.js, Express.js, Redis, STOMP, Socket.io, Kafka, MongoDB, MySQL, PostgreSQL, \\
Docker, Nginx, Github actions, Git, Linux, React.js, Next.js, Svelte, React-Native, Tailwind.

% \section*{Competitive Programming}
% \begin{itemize}[left=0.4cm, itemsep=0pt, topsep=1pt, partopsep=0pt]
%   \item Rated 1800+ on Leetcode (Top 6\%).
%   \item Achieved Rank 600 in Leetcode Weekly Contest 361.Backend
% \end{itemize}

\end{document}
